Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-04-14 ms.tex
adding todo notes from group meeting
changing frequency variable to omega rather than s
adding matching conditions

We employ an expansion in terms of spherical Bessel functions in $r$ and a Laplace expansion with the imaginary frequency variable $s=-i\omega$. The eigenvalues $s$ are real and negative for damped solutions to the time-dependent equation. The expansion for $J(r, \sigma, t)$ is

\be
\label{eq:jrsigmat_expansion}
J(r, \sigma, t) = \sum_{n=1}^{\infty} \int \frac{ds}{2\pi i} e^{st} j_0\left(\kappa_n r\right) J(n, \sigma, s).
\ee

The definition of the Laplace transform is

\be
J(n, \sigma, s) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{-st} J(r, \sigma, t).
\ee

@@

>>>>

TODO: Don't use s in these equations. Use damping rate omega here.
We employ an expansion in terms of spherical Bessel functions in $r$ and a Laplace expansion with the imaginary frequency variable $s=-i\omega$. The eigenvalues $s$ are real and negative for damped solutions to the time-dependent equation. The expansion for $J(r, \sigma, t)$ is

\be
\label{eq:jrsigmat_expansion}
J(r, \sigma, t) = -\sum_{n=1}^{\infty} \int \frac{d\omega}{2\pi} e^{-i\omega t} j_0\left(\kappa_n r\right) J(n, \sigma, \omega).
\ee

with

\be
J(n, \sigma, \omega) = \frac{2\kappa_n^2}{R} \int_0^R dr\ r^2 j_0(\kappa_n r) \int_0^\infty dt\ e^{i\omega t} J(r, \sigma, t).
\ee

@@

\be
 \left( \frac{3k\phi}{c}i\omega  -   \kappa_n^2 \right) J(n,\sigma,\omega)  &+& \left( \frac{k}{\Delta} \right)^2 \frac{d^2J(n,\sigma,\omega)}{d\sigma^2} = \frac{2\kappa_n^2}{R} (-1) \frac{\sqrt{6}}{4\pi} \frac{kE}{\Delta^2} \frac{1}{4\pi} \delta(\sigma - \sigma_s).
\ee

Now at $\sigma=\sigma_s$ continuity must be enforced in $J$ and the discontinuity in $dJ/d\sigma$  must be equal to

\be
\frac{\partial J_+}{\partial \sigma} - \frac{\partial J_-}{\partial \sigma} & = & 
- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3}.
\ee

Two numerical integrations are performed inward from large $\pm \sigma$ to the source $
\sigma_s$. The starting values of J are set to be $J_1$ and $J_2$ for the rightward and leftward integrations, respectively. Choices of these starting values are adjusted to ensure that the matching conditions at the source are met.

Separating the real and imaginary parts of the solution $J = J_r + i J_i$, we have

\be
 \frac{\partial^2 J_r}{\partial \sigma^2} &= & 
  \frac{\Delta^2 \kappa_n^2}{k^2} J_r  
 + 3 \omega \frac{\Delta^2 \phi}{kc}    J_i
\ee
and
\be
 \frac{\partial^2 J_i}{\partial \sigma^2} &= & 
  \frac{\Delta^2 \kappa_n^2}{k^2} J_i   
 - 3 \omega \frac{\Delta^2 \phi}{kc}    J_r.
\ee

The starting conditions are $J_{1,r}$, $J_{1,i}$, $J_{2,r}$, $J_{2,i}$.
The rightgoing and leftgoing integrations then produce $J_{-,r}$, $J_{-,i}$, $J^\prime_{-,r}$, $J^\prime_{-,i}$,  $J_{+,r}$, $J_{+,i}$, $J^\prime_{+,r}$, $J^\prime_{+,i}$, where the prime means $\partial/\partial \sigma$. The matching conditions are then
\be
J_{-,r} & =& J_{+,r} \\
J_{-,i} & =& J_{+,i} \\
 J_{+,r}^\prime - J_{+,r}^\prime & = & 
- \frac{\sqrt{6}}{8} n^2 \frac{E}{kR^3} \\
J_{+,i}^\prime - J_{+,i}^\prime & = & 0.
\ee
